### 2019-04-05 papers/journal/problem.tex
added clarification for the 3 problems and 4 envodings
Added additional diagram to fix the problem statement confusion

\noindent This section will present the different search problems of VTS.
%
We categorize the search problems into three different categories, search problem for existential condition, search problem for universal condition,
and performing synthesis on the incomplete VTS.

>>>>

\noindent This section will present the different search problems of VTS.
%
We categorize the search problem, Figure~\ref{fig:vts-search} into three different categories, search problem for existential condition, search problem for universal condition, and performing synthesis on the incomplete VTS. 
%
We will present two encodings for existential condition and one each for universal condition condition and synthesis.

\begin {figure}[!h]
\centering
\begin{adjustbox}{width=\columnwidth}
{\Large
%{	\scalefont{1.0}
%\forestset{parent color/.style args={#1}{
%		{fill=#1},
%		for tree={fill/.wrap pgfmath arg={#1!##1}{1/level()*80},draw=#1!80!darkgray}},
%	root color/.style args={#1}{fill={{#1!60!gray!25},draw=#1!80!darkgray}}
%}

\begin{forest}
 /tikz/every node/.append style={font=\sffamily,minimum size=1.0cm},
	for tree={
		edge+={->,thick},% uncomment for arrows
		draw,
		rounded corners,
		node options={align=center,},
		text width=1.7cm,
		calign=fixed edge angles, calign primary angle=-84,calign secondary angle=85,
	%	anchor=center,	
    %	calign=center,
	},
	where level=0{%
		parent anchor=children,
	}{%
		folder,
		grow'=0,
		if level=1{% this changes the edges from level 0 to nodes at level 1
			before typesetting nodes={child anchor=north},
			edge path'={(!u.parent anchor) -- ++(0,-5pt) -| (.child anchor)},
		}{},
	}
    [\textbf{VTS Search \\ Problems}, fill=white!20, parent, s sep=1mm,
	[\textbf{Existential Condition}, for tree={fill=fv, child}, 
	[BMC, for tree={fill=ai, child}]
	[SMT \\, for tree={fill=ai, child}]
	]
	[\textbf{Universal Condition}, for tree={fill=fv, child},
	[QBF, for tree={fill=ai, child}]
	]
	[\textbf{VTS Synthesis}, for tree={fill=fv,child}, 
	[Synthesis, for tree={fill=ai, child}]
	]
	]
\end{forest}
}
\end{adjustbox}
\vspace{0.01cm}

\begin{tikzpicture}
\begin{customlegend}[legend columns=-1,legend style={draw=none,column sep=1ex},legend entries={ \small Problem Statement, \small Encodings}]
\addlegendimage{fill=fv,area legend} 
\addlegendimage{fill=ai,area legend} 
%\addlegendimage{fill=ar,area legend}
%\addlegendimage{red,fill=black!50!red,ybar,ybar legend}
\end{customlegend}
\end{tikzpicture}

\caption{Overview of the VTS search problems with respective encodings}
\label{fig:vts-search}
\end{figure}
